Exposing Disputed Statements on the Web

### 2009-03-29 papers/uist_thinklink/thinklink.tex
Spellcheck. Fixed arrow bug in UI

Users provide all Think Link's information: they create new claims, mark new snippets, connect claims and snippets together.
Think Link is designed to support two primary usage scenarios: (i) Activists care strongly about a particular issue and combine Think Link with a search engine to find and mark snippets that make claims that they disagree with; and (ii) Sceptical Readers install Think Link as a browser extension to see when statements they read are disputed and find other sources tha tpresent alternative viewpoints.

@@

The design of Think Link was guided by two user studies in which we observed users' behaviour as they perfomed tasks fitting the usage scenarios for Activist and Sceptical Reader.

@@

Think Link builds on work in several different areas. The argumentation structure is influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}. The idea of highlighting potentially unstrustworthy information was applied to Wikipedia by WikiTrust~\cite{Adler2008a}. Tagging Systems~\cite{Marlow2006} influenced the way Think Link uses the community to collect and filter information. Clipping tools such as Internet Scrapbook~\cite{Sugiura1998} allow users to mark snippets on web sites.

@@

Videolyzer~\cite{Diakopoulos2008}\footnote{http:\\www.videolyzer.com} allows users to annotate and comment on political videos with accompanying textual transcriptions. A user can mark up a section of video for bias, accuracy, or rhetorical technique. Comments can include references to external sources that back up the argument being made. Like SpinSpotter, Videolyzer attaches annotations to a specific video section and does not attempty to gather multiple video sections that make a common contentious claim.

@@

The aim of the first study was to see how users normally browse the web and see their reactions to an early version of the Think Link argument graph. The aim of the second study was to evaluate user responses to an updated version of the interface and evaluate how users responded to seeing highlighted snippets on the page. At the end of each study, we asked each partipicant whether there were times in the past where they would have wanted to use Think Link. We present the results of the two studies together.

@@

For the first study we recruited twelve paid participants, five female, seven male, aged 18 to 52. Nine participants regularly posted to a blog. We recruited participants by posting an advert on craigslist\footnote{http://craigslist.org}.
Our intention was to recruit users who fit our ``sceptical reader'' and ``activist'' personas. In our advert, we asked people to tell us what kind of information they looked at on the web, and how they shared information with others. We selected participants who looked at information that was likely to be disputed (e.g. political commentry) and said they regularly shared information with friends. We avoided applications from people who were more interested in less disputed topics like social networking or sport.

@@

Study sessions took approximately fourty five minutes. Participants were seated at a single-screen workstation with the Firefox browser augmented with the Think Link extension. We first demonstrated Think Link's interface, and then asked them to browse web sites they normally use

>>>>

Users provide all Think Link's information: they create new claims, mark new snippets, connect claims and snippets together.
Think Link is designed to support two primary usage scenarios: (i) Activists care strongly about a particular issue and combine Think Link with a search engine to find and mark snippets that make claims that they disagree with; and (ii) Sceptical Readers install Think Link as a browser extension to see when statements they read are disputed and find other sources that present alternative viewpoints.

@@

The design of Think Link was guided by two user studies in which we observed users' behaviour as they performed tasks fitting the usage scenarios for Activist and Sceptical Reader.

@@

Think Link builds on work in several different areas. The argumentation structure is influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}. The idea of highlighting potentially untrustworthy information was applied to Wikipedia by WikiTrust~\cite{Adler2008a}. Tagging Systems~\cite{Marlow2006} influenced the way Think Link uses the community to collect and filter information. Clipping tools such as Internet Scrapbook~\cite{Sugiura1998} allow users to mark snippets on web sites.

@@

Videolyzer~\cite{Diakopoulos2008}\footnote{http:\\www.videolyzer.com} allows users to annotate and comment on political videos with accompanying textual transcriptions. A user can mark up a section of video for bias, accuracy, or rhetorical technique. Comments can include references to external sources that back up the argument being made. Like SpinSpotter, Videolyzer attaches annotations to a specific video section and does not attempt to gather multiple video sections that make a common contentious claim.

@@

The aim of the first study was to see how users normally browse the web and see their reactions to an early version of the Think Link argument graph. The aim of the second study was to evaluate user responses to an updated version of the interface and evaluate how users responded to seeing highlighted snippets on the page. At the end of each study, we asked each participant whether there were times in the past where they would have wanted to use Think Link. We present the results of the two studies together.

@@

For the first study we recruited twelve paid participants, five female, seven male, aged 18 to 52. Nine participants regularly posted to a blog. We recruited participants by posting an advert on craigslist\footnote{http://craigslist.org}.
Our intention was to recruit users who fit our ``sceptical reader'' and ``activist'' personas. In our advert, we asked people to tell us what kind of information they looked at on the web, and how they shared information with others. We selected participants who looked at information that was likely to be disputed (e.g. political commentary) and said they regularly shared information with friends. We avoided applications from people who were more interested in less disputed topics like social networking or sport.

@@

Study sessions took approximately forty five minutes. Participants were seated at a single-screen workstation with the Firefox browser augmented with the Think Link extension. We first demonstrated Think Link's interface, and then asked them to browse web sites they normally use
